Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-05 Paper.tex
Uncommenting \usepackage[utf8]{inputenc} so that ë shows in the PDF. Fixing definition of e in signing transactions to cross-reference to h(T).

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
%\usepackage[utf8]{inputenc}
%This character renders, so this shouldn't be needed: \DeclareUnicodeCharacter{C3}{\"{e}}
%For testing: \DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

We assert the functions $\mathtt{\small ECDSAPUBKEY}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSASIGN}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom} and \cite{ECDSAWikipedia}.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\ e & \equiv & \mathtt{\small HASH}(m) \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the aforementioned range). $e$ is the hash of the message $m$, using some cryptographic hash function such as SHA-3.\hypertarget{v}{It is assumed that $v$ is the `recovery id', a 1 byte value specifying the sign and finiteness of the curve point; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid.}

@@

The message hash, $h(T)$, to be signed is the Keccak hash of the transaction without the latter three signature components, formally described as $T_\mathbf{r}$, $T_\mathbf{s}$ and $\hyperlink{T w}{T_\mathbf{w}}$:
\begin{eqnarray}
L_S(T) & \equiv & \begin{cases}
(T_\mathbf{n}, T_\mathbf{p}, T_\mathbf{g}, T_\mathbf{t}, \hyperlink{T v}{T_\mathbf{v}}, T_\mathbf{i}) & \text{if} \; T_\mathbf{t} = 0\\
(T_\mathbf{n}, T_\mathbf{p}, T_\mathbf{g}, T_\mathbf{t}, \hyperlink{T v}{T_\mathbf{v}}, T_\mathbf{d}) & \text{otherwise}
\end{cases} \\
h(T) & \equiv & \mathtt{\small KEC}( L_S(T) )
\end{eqnarray}

>>>>

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
\usepackage[utf8]{inputenc}
%This character renders, so this shouldn't be needed: \DeclareUnicodeCharacter{C3}{\"{e}}
%For testing: \DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

We assert the functions $\mathtt{\small ECDSAPUBKEY}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSASIGN}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom} and \cite{ECDSAWikipedia}.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\ e & \equiv & \hyperlink{h T}{h(T)} \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the aforementioned range). \hypertarget{v}{It is assumed that $v$ is the `recovery id', a 1 byte value specifying the sign and finiteness of the curve point; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid.}

@@

\hypertarget{h T}{
The message hash, $h(T)$, to be signed is the Keccak hash of the transaction without the latter three signature components, formally described as $T_\mathbf{r}$, $T_\mathbf{s}$ and $\hyperlink{T w}{T_\mathbf{w}}$:
\begin{eqnarray}
L_S(T) & \equiv & \begin{cases}
(T_\mathbf{n}, T_\mathbf{p}, T_\mathbf{g}, T_\mathbf{t}, \hyperlink{T v}{T_\mathbf{v}}, T_\mathbf{i}) & \text{if} \; T_\mathbf{t} = 0\\
(T_\mathbf{n}, T_\mathbf{p}, T_\mathbf{g}, T_\mathbf{t}, \hyperlink{T v}{T_\mathbf{v}}, T_\mathbf{d}) & \text{otherwise}
\end{cases} \\
h(T) & \equiv & \mathtt{\small KEC}( L_S(T) )}
\end{eqnarray}
